---
title: "Be Curious Results"
author: "Leeds Clinical Trials Research Unit"
date: "07/05/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overall (suitable for 5+ years old)

This is a bar chart. It shows us all the data from the different people we surveyed at Be Curious this year. The chart can give us an early idea on whether there might be a link between the chocolate groups and the different levels of happiness.

Do you think there might be a link? Is everyone very happy? Are more people happy in Group A or Group B? Or are there a mix of answers?

```{r overall, echo=FALSE, fig.show="hold"}
data<-read.csv('Be curious 2022 participant data.csv')
data$Colour<-as.factor(data$Colour)
data$Group<-as.factor(data$Group)
data$How.Happy.Are.You.<-factor(data$How.Happy.Are.You., ordered=TRUE, labels=c("Not Happy","Happy","Very Happy"))

OverallPlotData <- data.frame(table(data$Group, data$How.Happy.Are.You.))
colnames(OverallPlotData) <- c("Chocolate Group", "Happy", "Freq")

library(ggplot2)
library(scales)
library(grid)
library(gridExtra)
library(tidyr)
library(gt)

OverallPlot <- ggplot(OverallPlotData, aes(fill=`Chocolate Group`, x=Happy, y=Freq)) + 
  geom_bar(position="dodge", stat="identity") + theme_minimal() + theme(plot.title = element_text(size = 12,hjust=0.5)) +
  scale_fill_brewer(palette="Paired") + 
  geom_text(aes(label=Freq), vjust=1.6, color="white", position = position_dodge(0.9), size=3.5) +
  labs(title="Current Happiness by Chocolate Groups", x="Current Happiness", y="Number of Participants")

OverallPlot

```
<br><br>

Or we could set the data up as a table:
```{r, echo=FALSE}
table<-spread(OverallPlotData,key=Happy,value=Freq)
table[,5]<-rowSums(table[,2:4])
colnames(table)[5]<-"Total"

tbl<-table %>%
  gt() %>%
    cols_width(
      ends_with("Happy") ~ px(100),
      Total ~ px(100)
    )

tbl
```
<br><br>

We can also summarise the data by colour group to see how many people from each group took part in the study. Do some colour groups have more people in than others?

```{r, echo=FALSE}
PlotColours = c("Sparkly Pink" = rgb(255,0,102, maxColorValue=255), "Orange" = rgb(255,122,31, maxColorValue=255), "Dark Blue"= rgb(68,117,161, maxColorValue=255), "Sparkly Purple"= rgb(153,51,102, maxColorValue=255), "Red"= rgb(255,0,0, maxColorValue=255), "Light Blue"= rgb(190,215,239, maxColorValue=255), "Teal" = rgb(0,128,128, maxColorValue=255), "Yellow" = rgb(255,255,25, maxColorValue=255), "Purple" = rgb(204,153,255, maxColorValue=255), "Sparkly Red" = rgb(255,0,0, maxColorValue=255), "Pink" = rgb(255,153,204, maxColorValue=255), "Green" = rgb(146,208,80, maxColorValue=255))
PlotLabels = c("Sparkly Pink" = "Sparkly\nPink" , "Orange" = "Orange", "Dark Blue"= "Dark\nBlue", "Sparkly Purple"= "Sparkly\nPurple", "Red"= "Red", "Light Blue"= "Light\nBlue", "Teal" = "Teal", "Yellow" = "Yellow", "Purple" = "Purple", "Sparkly Red" = "Sparkly\nRed", "Pink" = "Pink", "Green" = "Green")

SummaryPlot <- ggplot(data=data, aes(x=Colour,fill=Colour)) +
  geom_bar(stat="count") +
  geom_text(stat="count", aes(label=..count..), vjust=1.6, color="black", position = position_dodge(0.9), size=3.5) +
  theme_minimal() +
  scale_fill_manual(values = PlotColours, aesthetics = "fill") +
  theme(axis.text.x = element_text(size=10), legend.position = "none", plot.title = element_text(size = 12,hjust=0.5)) +
  labs(title="Population Summary", y= "Number of people in each group", x = "Colour Group") + labs(fill="Colour Group") +
  geom_point(aes(x="Sparkly Pink", y=0), shape=8) +
  geom_point(aes(x="Sparkly Red", y=0), shape=8) +
  geom_point(aes(x="Sparkly Purple", y=0), shape=8) +
  scale_x_discrete(labels=PlotLabels)

SummaryPlot
```


Wasn't sure whether to have shiny element here so you could look at by colour group but don't know how to write this up, feel free to include if you know!

```{r pressure, echo=FALSE}

```

### Statistical test (suitable for X-Y years old)

While the graphs give us an early idea about the data we've collected, the best way to find out if there's a difference in happiness between the two chocolate groups is to use a statistical test. This will to help us decide if there might be a link (or association) between chocolate group and happiness. From the people we asked at Be Curious, our results were...

```{r echo=FALSE}
chisq <- chisq.test(table(data$Group, data$How.Happy.Are.You.))
fishers <- fisher.test(table(data$Group, data$How.Happy.Are.You.))

if(chisq$expected[1,1] < 5 || chisq$expected[1,2] < 5 || chisq$expected[1,3] < 5 || chisq$expected[2,1] < 5 || chisq$expected[2,2] < 5 || chisq$expected[2,3] < 5){
  if(fishers$p.value<0.05){ans <- "Fishers Test: Happiness and Chocolate Group are not independent"}
  else{ans <- "Fishers Test: Happiness and Chocolate Group are independent"}
  
}else{
  if(chisq$p.value<0.05){ans <- "Chi-Squared Test: Happiness and Chocolate Group are not independent"}
  else{ans <- "Chi-Squared Test: Happiness and Chocolate Group are independent"}
}
ans
```
<!-- #!DELETE ONE OF THESE ACCORDING TO THE RESULT! -->
This means that there is not enough evidence to say that one chocolate group makes people happier than another. How did this compare to your thoughts from looking at the bar charts?

This means there is evidence to say that there is a difference in how happy the two chocolate groups make people. How did this compare to your thoughts from looking at the bar charts?

<!-- #!DO NOT DELETE FROM HERE! -->
The issue from this test is that if we find the chocolate group to be independent, we don't know which group makes people happier than the other, all we would know is that there is a difference. We may also want to know whether there is a difference in peoples' answers based on their age, happiness before eating chocolate or their chocolate preferences.
<br><br>

### Statistical model (suitable for X-Y years old)

We can find out the answers to all of these questions too! To do this, we will use a mathematical model which will produce odds ratios from which we can make our conclusions. Odds ratios show us how much more likely someone in one group (e.g. chocolate group, age group, happiness at the start of the activity) is to be happy after eating their chocolate compared to another group.

If there is no difference in happiness between the two chocolate groups then the odds ratio will be 1, we would interpret this result as 'the type of chocolate you have does not affect your happiness.' If the odds ratio is greater than 1, this means a person is more likely to be happy in Group B than in Group A. If the odds ratio is lower than 1 then a person is less likely to be happy in Group B  than in Group A. When making our conclusion, it is important we also take into account the 95% confidence interval of the odds ratio, that is the range of values that we are 95% confident the odds ratio sits between.